Discrete Quantum Theories and Computing

### 2018-11-22 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

Since the probability induced by the different beam splitters are
correlated, it is more natural to define one quantum event space~$\events$
containing all possible classical event spaces using different beam
splitters. However, simply taking the union of all event spaces is
bad because two events might appear different but representing the
same situation. For example, if we take the complement on the both
sides of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
we will have
\begin{equation}
\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
\end{equation}
that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same. To
simplify our discussion, we want to identify two classical events
$\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
as the same quantum event. Since the projectors generated by these
two events are equal as operators, i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$,
given any classical event~$E$, we can follow the same idea to define
the quantum event corresponding to $E$ as the projector generated
by $E$
\begin{equation}
\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
\end{equation}
with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$, and
a quantum event space~$\events$ is the set of all projectors on
a given Hilbert space. This definition is really capture our intuition
because of the following lemma.

@@

\noindent In another word, when sending a particle to a Stern-Gerlach
type experiment, we will get a quantum probability measure of the
form $\Tr\left(\rho P\right)$ for some operator~$\rho$.

Recall in Sec.~\ref{CQC1qubitBloch.sec}, the status of our system
can be characterized by

@@

After defining a QPMFF~$\mu$, we would like to follow the idea of
Gleason's theorem to see whether we might trace back from $\mu$ to
a pure or mixed state, and summarize this correspondence as a discrete
Born rule. When $p=D=3$, there are indeed some correspondence between
QPMFFs and states. However, when $D=3$ and $p=7$, we have numerical
verified that the only QPMFF $\mu:\events_{7^{2}}\rightarrow\left[0,1\right]$
is
\begin{equation}
\mu\left(P\right)=\begin{cases}
0 & \textrm{if }P=\mathbb{0}\,;\\
\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimensional projector;}\\
\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimensional projector;}\\
1 & \textrm{if }P=\mathbb{1}\,.
\end{cases}
\end{equation}
As we computed in Eq.~(\ref{eq:numberOfIrreducibleStates}), the
number of unique irreducible pure states in $\ff{7^{2}}^{3}$ is 
\begin{equation}
\frac{7^{3-1}\left(7^{3}-\left(-1\right)^{3}\right)}{7+1}=2107\label{eq:numberOfIrreducibleStates-7-3}
\end{equation}
which is much more then one, the number of QPMFF. Since we don't have
enough QPMFF to correspond even pure states, there is no discrete
Born rule in this case. In general, we conjecture that QPMFF is always
unique for $D\ge3$ except $D=p=3$.

>>>>

Since the probability induced by the different beam splitters are
correlated, it is more natural to define one quantum event space~$\events$
containing all possible classical event spaces using different beam
splitters. However, simply taking the union of all event spaces is
bad because two events might appear different but representing the
same situation. For example, if we take the complement on the both
sides of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
we will have
\begin{equation}
\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
\end{equation}
that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same. To
simplify our discussion, we want to identify two classical events
$\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
as the same quantum event. Since the projectors generated by these
two events are equal as operators, i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$,
given any classical event~$E$, we can follow the same idea to define
its quantum event as the projector generated by $E$
\begin{equation}
\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
\end{equation}
with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$. This
function $\varphi$ well glues all classical event spaces into one
quantum event space~$\events$, the set of all projectors on a given
Hilbert space, because of the following lemma.

@@

Although Gleason's theorem can correspond every quantum probability
measure to a unique mixed state~$\rho$, it doesn't explain whether
this state $\rho$ characterizing the state of particle sending to
a Stern-Gerlach type experiment. For example, a variant of quantum
probability measure has only one instance defined in Eq.~\ref{eq:QPMFF37}.
This instance predicts all outcomes to be equally probable which intuitively
corresponds to the mixed state $\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$
in its space. However, ignoring the input state and always predicting
equally probable is not a sensible quantum theory.

Let $\ket{\Phi}$ characterize the state of particle sending to a
Stern-Gerlach type experiment, and $\muB_{\Phi}$ be the corresponding
quantum probability measure of the resulting events.

To find a sensible correspondences between quantum probability measures
and the input states,

\noindent , when sending a particle to a Stern-Gerlach type experiment,
we will get a quantum probability measure of the form $\Tr\left(\rho P\right)$
for some operator~$\rho$.

Recall in Sec.~\ref{CQC1qubitBloch.sec}, the state of the particle
can be characterized by a pure state $\ket{\Psi}\in\Hilb$ or more
generally a mixed state~$\rho'$. Although the function $\Tr\left(\rho P\right)$
is parametrized by

@@

After defining a QPMFF~$\mu$, we would like to follow the idea of
Gleason's theorem to see whether we might trace back from $\mu$ to
a pure or mixed state, and summarize this correspondence as a discrete
Born rule. When $p=D=3$, there are indeed some correspondence between
QPMFFs and states. However, when $D=3$ and $p=7$, we have numerical
verified that the only QPMFF $\mu:\events_{7^{2}}\rightarrow\left[0,1\right]$
is
\begin{equation}
\mu\left(P\right)=\begin{cases}
0 & \textrm{if }P=\mathbb{0}\,;\\
\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimensional projector;}\\
\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimensional projector;}\\
1 & \textrm{if }P=\mathbb{1}\,.
\end{cases}\label{eq:QPMFF37}
\end{equation}
As we computed in Eq.~(\ref{eq:numberOfIrreducibleStates}), the
number of unique irreducible pure states in $\ff{7^{2}}^{3}$ is 
\begin{equation}
\frac{7^{3-1}\left(7^{3}-\left(-1\right)^{3}\right)}{7+1}=2107\label{eq:numberOfIrreducibleStates-7-3}
\end{equation}
which is much more then one, the number of QPMFF. Since we don't have
enough QPMFF to correspond even pure states, there is no discrete
Born rule in this case. In general, we conjecture that QPMFF is always
unique for $D\ge3$ except $D=p=3$.
